Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-11 write-ups/PLDI/paper.tex
Oops.

\paragraph{Graph traversal example} \mylongfig\ref{fig:graphsearch} shows the
skeleton of a frontier-based graph traversal algorithm; such algorithms have
been shown to be execute efficiently on GPUs~\cite{...}.
The kernel is
given three arguments in global memory: a graph structure, and two
arrays that can contain graph nodes. Initially, $\keyword{n0}$ contains the
starting nodes to process. Threads keep three local variables: $\keyword{level}$, which indicates the frontier level currently being
processed, and $\keyword{in\_nodes}$ and $\keyword{out\_nodes}$, which point to
distinct node arrays. The nodes to be
processed for the current frontier are contained in $\keyword{in\_nodes}$, while $\keyword{out\_nodes}$ contains
the nodes to be processed during the next frontier.

>>>>

\paragraph{Graph traversal example} \myfiglong\ref{fig:graphsearch} shows the
skeleton of a frontier-based graph traversal algorithm; such algorithms have
been shown to be execute efficiently on GPUs~\cite{...}.
The kernel is
given three arguments in global memory: a graph structure, and two
arrays that can contain graph nodes. Initially, $\keyword{n0}$ contains the
starting nodes to process. Threads keep three local variables: $\keyword{level}$, which indicates the frontier level currently being
processed, and $\keyword{in\_nodes}$ and $\keyword{out\_nodes}$, which point to
distinct node arrays. The nodes to be
processed for the current frontier are contained in $\keyword{in\_nodes}$, while $\keyword{out\_nodes}$ contains
the nodes to be processed during the next frontier.
